\section{Preliminaries, Definitions}\label{sec:prelims}

We begin by introducing the necessary definitions and terminology, as
well as a few observations about the mathematical objects of interest
which will be of use later.  We carefully lay out these definitions so
as to align with an intuitive understanding of the concepts and to
appease the astute reader who may be concerned with edge cases,
geometric weirdness, and nonmeasurability.

\begin{definition}
A \textbf{region} $\Omega$ is an non-empty open set together with its
boundary such that the region is measurable, its boundary is
measurable, and it is connected.
\end{definition}

We choose this definition so that concepts of the `area' and
`perimeter' of a region are well-defined concepts.  Throughout, we
restrict our attention to the plane $\mathbb{R}^2$ (or $\C$ if one
prefers) and the surface of the unit sphere $\mathbb{S}^2$ equipped
with the standard measures and metrics.  We leave the consideration of
other surfaces, measures, and metrics to future work.

\begin{definition}
A \textbf{compactness score function} $\mathcal{C}$ is a function from
the set of all regions to the positive real numbers.  We adopt the
convention that a region with a \textit{higher} compactness score is
\textit{more} compact, and this naturally induces a partial order over
the set of all regions, where $A$ is at least as compact as $B$ if and
only if $\mathcal{C}(A)\geq \mathcal{C}(B)$.
\end{definition}

The final major definition we need is that of a \textit{map
projection}.  In reality, the regions we are interested in comparing
sit on the surface of the Earth (i.e. a sphere), but these regions are
often examined as being projected onto a flat sheet of paper or
computer screen, and which means that the regions drawn in any flat
map object are subject to such a projection.

\begin{definition}
A \textbf{map projection} $\varphi$ is a local diffeomorphism from the
sphere to the plane.  This means that $\varphi$ is continuous,
$\varphi^{-1}$ exists and is also continuous, and the image of a
region in the sphere is a region in the plane.
\end{definition}

\begin{definition}
We use the word \textbf{transformation} [of the plane/sphere] to mean
to a diffeomorphism from the plane or sphere to itself.
\textbf{Linear transformations} of the plane are those parametrized by
invertible $2{\times}2$ matrices, and \textbf{affine linear
transformations} are those transformations which are the composition
of a linear transformation and a translation of the plane.
\end{definition}

Since the image of a region under a map projection $\varphi$ is also
a region, we can examine the compactness score of that region both 
before and after applying $\varphi$, and this is the heart of the
problem we address in this paper.  We demonstrate, for several
standard choices of compactness scores $\mathcal{C}$, that the order
induced by $\mathcal{C}$ is different than the order induced by
$\mathcal{C}\circ\varphi$ for \textit{any} choice of map projection
$\varphi$.

For each of the compactness scores we analyze, our proof that no map
projection can preserve their order follows a similar recipe.  We
first use the fact that any map projection which preserves an ordering
must preserve the \textit{maximizers} of that ordering, meaning that
if $\Omega$ is a region for which $\mathcal{C}(\Omega)\geq
\mathcal{C}(\Sigma)$ for all regions $\Sigma$, then it must at the
very least be the case that $\mathcal{C}(\varphi(\Omega))\geq
\mathcal{C}(\varphi(\Sigma))$ if $\varphi$ preserves $\mathcal{C}$'s
ordering.

Using this fact, we can restrict our attention to those map
projections which preserve the maximizers in the induced ordering,
then argue that any projection in this restricted set must permute the
order of scores of some pair of regions.
