\subsection{Organization of the Paper}


For each of the compactness scores we analyze, our proof that no map
projection can preserve their order follows a similar recipe. We
first use the fact that any map projection which preserves an ordering
must preserve the \textit{maximizers} in that ordering.  In other words,
if there is some shape which a score says is `the most compact' on the sphere 
but this is not the case in the plane after applying a projection, then whatever 
shape \textit{does} get sent to `the most compact' shape in the plane leapfrogs 
the first shape in the induced ordering.

Using this observation, we can restrict our attention to those map
projections which preserve the maximizers in the induced ordering,
then argue that any projection in this restricted set must permute the
order of scores of some pair of regions.


\paragraph{Preliminaries}
We first introduce some definitions and results which we will use to prove our 
three main theorems.  Since spherical geometry differs from the familiar planar geometry, 
we carefully describe a few properties of spherical lines and triangles to build some intuition 
in this domain. 


\paragraph{Convex Hull}
For the convex hull score, we first 
show that any projection which preserves the maximizers of the convex hull score 
ordering must maintain certain geometric properties of shapes and line segments 
between the sphere and the plane.  Using this, we demonstrate that no 
map projection from the sphere to the plane can preserve these properties, and therefore 
no such convex hull score order preserving projection exists.



\paragraph{Reock}
For the Reock score, we follow a similar tack, first showing that any 
order-preserving map projection must also preserve some geometric properties 
and then demonstrating that such a map projection cannot exist.





\paragraph{Polsby-Popper}
To demonstrate that there is no projection which maintains the score ordering induced by the Polsby-Popper score, we again use properties of spherical geometry.  In this setting, we leverage the 
difference between the \textit{isoperimetric inequalities} on the sphere and in the plane in order to 
demonstrate that the Polsby-Popper score, as given, is not scale-free on the sphere.  We then readjust 
our definition to a more robust version of the isoperimetric quotient and use the machinery developed 
in the Reock section to demonstrate that no map projection exists which preserves the ordering induced by this score, either.

\paragraph{Generalizations and Discussion}
While we prove our results in the contexts of three specific scores, the machinery we develop along the way can be broadly applied to other kinds of compactness scores.  Rather than present these as independent theorems, we offer them as exercises to an interested reader.  Most of the machinery needed to prove them is included in this paper; some follow almost immediately as corollaries and others require more careful digestion of the tools and techniques used for the three scores we dissect.


