\section{Introduction}\label{sec:intro}

Striving for the \textit{geometric compactness} of legislative
districts is a traditional principle of redistricting, and, to that
end, many jurisdictions have included the criterion of compactness in
their legal code for drawing districts.  However, there is no
agreed-upon definition for what makes a district compact or not.
Several competing mathematical definitions have emerged over the past
two centuries, including the \textit{Polsby-Popper score}, \cut{which
measures the ratio of a district's area to the square of its
perimeter,}  the \textit{convex hull score}, \cut{which measures the ratio
of the area of a district to the smallest convex region containing it},
and the \textit{Reock score}, \cut{which measures the ratio of the area of
a district to the smallest circle containing it}.  Each of these
measures is appealing at an intuitive level, since they each assign to
a district a single scalar value between zero and one, allowing easy
comparisons between proposed redistricting plans. Additionally, the
mathematics underpinning each is widely understandable by the relevant
parties, including lawmakers, judges, advocacy groups, and the general
public.  None of these measures is perfect, however\cit.  \cut{
For each, it is not difficult to construct a 
mathematical counterexample for which
a human's intuition and the score's evaluation of a shape's
compactness differ, such as a circle with slightly perturbed boundary
for the Polsby-Popper measure and a very long, thin rectangle for the
convex hull measure. } Additionally, these scores often do not agree.
The long, thin rectangle has a very good convex hull score, but a very
poor Polsby-Popper score.  These issues are well-studied by political
scientists and mathematicians alike
\cite{polsby1991third,frolov1975shape,maceachren1985compact}.

In this paper, we propose a further critique of these measures, namely
\textit{sensitivity under the choice of map projection}.  Each of the
compactness scores named above is defined as a tool to evaluate
geometric shapes in the plane, but in reality we are interested in
analyzing shapes which sit on the surface of the planet Earth, which
is (roughly) spherical\cit.  When a shape is assigned a compactness score,
it is implicitly done with respect to some choice of map projection.
We show, both mathematically and empirically, that this may have
serious consequences for the evaluation of compactness.  In
particular, we define the analogue of the Polsby-Popper, convex hull,
and Reock scores on the sphere, and demonstrate that for any choice of
map projection, there are two regions, $A$ and $B$, such that $A$ is
more compact than $B$ on the sphere but $B$ is more compact than $A$
when projected to the plane.
