\mute{

\begin{proof}[Proof of~\ref{Thm1}]
  Let $C\subset U$ be an open cap of $S^2$, 
  and $B\subset C$ some other cap. Let $A'\subset \vphi(B)\subset \vphi(C)\subset \R^2$ 
  be some disk, and $A = \vphi^{-1}(A')$. Since $\vphi$ is a 
  diffeomorphism, it follows that 
  $\vphi(B),\vphi(C),A$ are open sets with smooth boundary.
  \begin{Claim}
    $A'$ maximizes Polsby-Popper score 
    in $\vphi(C)$, but $A$ does not maximize Polsby-Popper 
    score in $C$. 
  \end{Claim}
  \begin{proof}
    $A'$ maximizes Polsby-Popper score in $\vphi(C)$, because 
    it is a disk in the plane. On the sphere, let 
    $\hat A$ be the cap with equal area to $A$. By 
    \cref{PP_S2}, it follows that 
    $\PP_S(\hat A)\ge \PP_S(A)$. Since $A\subset B$ 
    it follows by construction that 
    $\mathrm{Area}(\hat A)\le \mathrm{Area}(B)$, meaning 
    that $\hat A$ is a cap with geodesic radius 
    smaller than $B$'s.

    By the computation in \cref{Caps_Eg}, it follows
    that:
    \begin{align*}
      \PP_S(A)\le \PP_S(\hat A)\le \PP_S(B)< \PP_S(C)
    \end{align*}
    as desired.
  \end{proof}
  Notice that the claim proves the 
  theorem, as any diffeomorphism 
  preserving orders of Polsby-Popper scores would 
  preserve maximal regions in the ordering.
\end{proof}
\abn{muted the second proof with measures and other bs}

\begin{proof}
  TODO: proof 2: delete?
  \begin{Claim}

  \end{Claim}
  \begin{proof}
  \end{proof}
  Let $C\subset U$ be an open ball in $S^2$. Let $A\subset C$ be some 
  region, and $B$ be a ball such that $\mu_S(A)=\mu_S(B)$. We note 
  that since $Area(B)< Area(C)$, we can position $B$ such that 
  $B\subset C$. Moreover, by By \cref{PP_S2}, 
  it follows that $\PP_S(B)\ge \PP_S(A)$. 

  Note that $\PP_S(B(r))$ is monotonically strictly 
  increasing with the radius $r$, as shown by 
  \cref{Caps_Eg}. Note that 
  $\sup_{A\subset C} \PP_S(A)=\PP_S(C)$, simply by 
  taking an increasing sequence of balls whose radii 
  converge to that of $C$. Since $\PP_S(A) \le \PP_S(B) < \PP_S(C)$, 
  there does not exist a maximizer of $\PP_S$ within $C$.

  However, on the plane, every open region has a 
  maximizer of $\PP$. In particular, these maximizers are the open discs.
  Suppose that $A'$ is one such open disc in $\phi(C)$. 
  Then $\PP_{\R^2}(\vphi(A')) < \PP_{\R^2}(C)$, so there is an open cap $B \subset C$ 
  so that $\PP_{\R^2}(\vphi(A')) < \PP_{\R^2}(B)$.

  Let $A = \vphi(A')$. Then $\PP_{\R^2}(A) < \PP_{\R^2}(B)$, but 
  $\PP_{\R^2}(\phi(A)) = \PP_{\R^2}(A') \geq \PP_{\R^2}(\phi(B))$, which is the
  conclusion of the theorem.
  
\end{proof}
}





\mute{
Throughout this note, we will write 
$A_{\eps} = \cup_{a\in A}B_{a,\eps}$, the $\eps$-thickening 
of $A$.
This theorem will follow from a crucial lemma due to 
\cite{PP_Sphere}:
\begin{Lemma}\label{Cite_Lemma}
  Let $A$ be a closed subset of $S^2$, and let $B$ be a ball in 
  $S^2$ such that $\mu_S(A)=\mu_S(B)$. Then for every 
  $\eps>0$, $\mu(A_{\eps})\ge \mu(B_{\eps})$.
\end{Lemma}
\begin{Lemma} \label{Tube_Lemma}
  Let $A\subset S^2$ be some compact region. Then
  \begin{align*}
    \mu_S(A_{\eps}) = \mu_S(A)+\eps \nu_S(\del A)+O(\eps^2)
  \end{align*}
\end{Lemma}
\begin{proof}
  sketch: do it for polygons, then pick a sequence of polygons $A_n$ 
  converging to $A$ in Hausdorff measure. Then 
  $(A_n)_{\eps}\to A_{\eps}$ in Hausdorff measure so 
  $vol(A_n\eps)\to vol(A_{\eps})$. But 
  $Vol(A_n)\to Vol(A)$ by dominated convergence, and 
  $Perim(A_n)\to Perim(A)$ by rectifiability, so
  \begin{align*}
    Vol(A_{\eps})
    =\lim Vol((A_n)_{\eps})
    =\lim Vol(A_n)+\eps Perim(A_n)+O(\eps^2)
    =Vol(A_{\eps})+\eps Perim(A_{\eps})+O(\eps^2)
  \end{align*}
\end{proof}
\begin{Corollary}
  If $A$ is a closed subset of $S^2$, and $B$ is a ball in 
  $S^2$ with $\mu_S(A)=\mu_S(B)$, then 
  $\nu_S(\del A)\ge \nu_S(\del B)$.
\end{Corollary}
\begin{proof}
  By \cref{Tube_Lemma}, we have:
  \begin{align*}
    \mu_S(A_{\eps}) &= \mu_S(A)+\eps\nu_S(A)+O(\eps^2)\\
    \mu_S(B_{\eps}) &= \mu_S(B)+\eps\nu_S(B)+O(\eps^2)
    =\mu_S(A)+\eps\nu_S(B)+O(\eps^2)
  \end{align*}
  By \cref{Cite_Lemma}, 
  $\mu_S(A_{\eps})\ge \mu_S(B_{\eps})$, it follows that:
  \begin{align*}
    \eps\nu_S(A)\ge \eps\nu_S(B)+O(\eps^2)
  \end{align*}
  Dividing by $\eps$ and passing to the limit as $\eps\to 0$ 
  gives the desired result.
\end{proof}
\begin{Corollary} \label{Main_Lemma}
  Balls in $S^2$ minimize Polsby-Popper ratios.
\end{Corollary}
\begin{proof}
  By~\cref{Cite_Lemma}, balls minimize perimeters 
  in their volume class, and hence, maximize Polsby-Popper ratios.
\end{proof}
}

\mute{
  Balls minimize perimeters in their volume class, and hence 
  maximize Polsby-Popper ratios.
}